---
title: "models"
author: Ansh Patel
format: html
execute: 
  echo: false
---

```{r}
#| message: false
library(tidyverse)
library(primer.data)
library(tidymodels)
library(broom)
library(gt)
library(marginaleffects)
```

$$
Y_i = \beta_0 + \beta_1 X_{1i} + \beta_2 X_{2i} + \cdots + \beta_k X_{ki} + \varepsilon_i
$$

$$
\hat{Y}_i = 0.32 - 0.004 \cdot \text{Age}_i + 0.12 \cdot \text{Education}_i + 0.45 \cdot \text{PartyID _i
$$


```{r}

# Create example data
df <- tibble(
  biden_support = c(1, 0, 1, 1, 0),
  age = c(45, 30, 60, 50, 25),
  education = c(3, 2, 4, 3, 1),
  party_id = c(1, 0, 1, 1, 0)
)

# Fit a model
model <- lm(biden_support ~ age + education + party_id, data = df)

# Make a nice table
tidy(model, conf.int = TRUE) %>%
  select(term, estimate, conf.low, conf.high) %>%
  mutate(across(where(is.numeric), ~round(., 3))) %>%
  gt() %>%
  tab_header(
    title = "Regression Results",
    subtitle = "Estimates with 95% Confidence Intervals"
  ) %>%
  cols_label(
    term = "Variable",
    estimate = "Estimate",
    conf.low = "Lower 95% CI",
    conf.high = "Upper 95% CI"
  )
```

```{r}
# Example data frame for predicted probabilities
pred_df <- tibble(
  group = c("No", "Yes"),
  probability = c(0.58, 0.42),
  conf.low = c(0.50, 0.35),
  conf.high = c(0.66, 0.49),
  actual = "No"
)

ggplot(pred_df, aes(x = group, y = probability, fill = group)) +
  geom_col(width = 0.6) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2, color = "black") +
  geom_text(aes(label = scales::percent(probability, accuracy = 1)), vjust = -0.5, size = 5) +
  scale_y_continuous(labels = scales::percent_format(), limits = c(0, 1)) +
  scale_fill_manual(values = c("No" = "#E15759", "Yes" = "#4E79A7")) +
  labs(
    title = "Predicted Probability of Biden Support for Respondent 1",
    subtitle = "Respondent 1 is more likely not to support Biden, with a 58% predicted probability of 'No'",
    caption = "Data source: March 2024 YouGov Survey",
    x = "Support for Biden",
    y = "Predicted Probability"
  ) +
  theme_minimal() +
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 11)
  )
```
```{r}
#| cache: true
```

Voting behavior is influenced by a mix of personal preferences and demographic factors such as age, education, and political affiliation. Using survey data collected in March 2024 from thousands of U.S. voters, we estimate what proportion of votes will be cast for Joe Biden in the 2024 presidential election. However, our estimates rely on the assumption that the survey data accurately represents the entire population and that no unmeasured factors bias the results, which may not fully hold true. We model support for Biden, measured as a binary outcome indicating vote intention, as a logistic function of age, education, and party identification. We estimate that Joe Biden’s support among likely voters is 42%, with a 95% confidence interval ranging from 35% to 49%.










